Learning Auditory Similarities Between Instrumental Playing Techniques

### 2018-01-29 paper/lagrangeSpontaneousSimilarity2017.tex
last comments on this version of the paper

To do so, one can first consider the linear discriminant analysis (LDA) \cite{duda2000pattern} to project the data into a representational space of $C-1$ dimensions with $C$ being the number of clusters of the reference. In our case study, the reference is the partition of \ipts provided by a subject during experiment 2. The projection computed using this method is such that the ratio of the between-class distance to the within-class distance is maximized, thus achieving maximum discrimination between elements of different clusters.

@@

\vl{The paragraph above is the most important in the whole paper, and it deserves more attention. @writing}

@@

\vl{What does "safely" mean here? We are at the epicenter of the paper here, every word matters. @writing}

@@

Our problem is thus cast into a ranking problem, where from several candidates, the algorithm is asked to provide a ranking list of those candidates, sorted by similarity.

@@

\vl{The mel scale has a varying quality factor, so I don't see how this can be right.}
\vl{I understand what "logarithmically compressed" and "normalized using the median" because I worked on this before but,
for someone who is less experienced, this might not be precise enough.}

@@

\begin{table}
  \caption{Precision achieved by the different settings. Numbers in bold face indicate best performance. \vl{Why are the results with TST, LMNN, and "reference" commented? Do they correspond to same rater between training and evaluation? @methodology}}
  \label{tab:res1}
  \begin{center}
\begin{tabular}{lllc}
features & projection & reference & precision (\%) \\
  \hline
  MFCCs & - & - &   85.07 $\pm$ 6.19 \\
  MFCCs & LDA &  consensus  &   81.50 $\pm$ 7.65 \\
MFCCs & LMNN & multiple & 86.31 $\pm$ 5.91 \\
MFCCs & LMNN & consensus &   86.22 $\pm$ 5.92 \\
% MFCCs & LMNN & reference &   86.18 $\pm$ 6.05 \\
TST & - & - &   87.01 $\pm$ 5.81 \\
TST & LDA & consensus &   80.95 $\pm$ 10.37 \\
TST & LMNN  & multiple  &   93.31 $\pm$ 3.92 \\
TST & LMNN & consensus &   \textbf{94.80 $\pm$ 3.26} \\
% TST & LMNN & reference &   98.09 $\pm$ 1.28 \\
\end{tabular}
\end{center}
\end{table}

>>>>

\vl{I am a bit wary about not giving proper names to the two experiments, but instead calling them "experiment 1" and "experiment 2".
How about "expert judgments of uniqueness" versus "crowdsourced judgments of similarity"? @writing}

To do so, one can first consider the linear discriminant analysis (LDA) \cite{duda2000pattern} to project the data into a representational space of $(C-1)$ dimensions, with $C$ being the number of clusters of the reference. In our case study, the reference is the partition of \ipts provided by a subject during experiment 2. The projection computed using this method is such that the ratio of the between-class distance to the within-class distance is maximized, thus achieving maximum discrimination between elements of different clusters.

@@

\vl{The paragraph above is the most important in the whole paper, and it deserves more attention. How do these three solutions differ? Which one was chosen in the end? Did it make a significant difference in NMI? Is the consensus clustering shown somewhere in the paper? Is it related to the dendrogram in Appendix B? I have so many questions. @writing}

\vl{I'm afraid there is also a methodological problem here.
We need to have a hold-out set of IPTs to evaluate the performance of the clustering algorithm after having trained the metric learning algorithm.
@methodology @computation}

@@

\vl{What does "safely" mean here? We are at the epicenter of the paper here: every word matters. @writing}

@@

Our problem is thus cast into a ranking problem, where from several candidates, the algorithm is asked to provide a ranked list of those candidates, sorted by similarity.

@@

\vl{The mel scale has a varying quality factor, so I don't see how this can be right.}
\vl{I understand what "logarithmically compressed" and "normalized using the median" because I did work on this before but,
for someone who is less experienced, this might not be precise enough.}

@@

\begin{table}
  \caption{Precision achieved by the different settings. Numbers in bold face indicate best performance. \vl{What does these variances correspond to? Variance across raters, across IPTs, across instances of each IPT? Furthermore, why are the results with TST, LMNN, and "reference" commented? Do they correspond to same rater between training and evaluation? @methodology @writing}}
  \label{tab:res1}
  \begin{center}
\begin{tabular}{lllc}
features & projection & reference & precision (\%) \\
  \hline
  MFCCs & - & - &   85.07 $\pm$ 6.19 \\
  MFCCs & LDA &  consensus  &   81.50 $\pm$ 7.65 \\
MFCCs & LMNN & multiple & 86.31 $\pm$ 5.91 \\
MFCCs & LMNN & consensus &   86.22 $\pm$ 5.92 \\
% MFCCs & LMNN & reference &   86.18 $\pm$ 6.05 \\
TST & - & - &   87.01 $\pm$ 5.81 \\
TST & LDA & consensus &   80.95 $\pm$ 10.37 \\
TST & LMNN  & multiple  &   93.31 $\pm$ 3.92 \\
TST & LMNN & consensus &   \textbf{94.80 $\pm$ 3.26} \\
% TST & LMNN & reference &   98.09 $\pm$ 1.28 \\
\end{tabular}
\end{center}
\end{table}
